Variation in use of East Asian Late Paleolithic weapons: A study of tip cross-sectional area of stemmed points from Korea

### 2022-05-26 analysis/paper/paper.Rmd
add site info and create the site map

```{r}
library(readxl)
library(here)
library(tidyverse)
library(ggbeeswarm)

@@

@@

ggplot (tcsa,
        aes(0.3, 
            min_tcsa)) +
  # show regions for tools from Table 3 of Lomabrd 2021
  # https://www-sciencedirect-com.offcampus.lib.washington.edu/science/article/pii/S0277379121002286
    annotate("rect", 
           xmin = 0.1,
           xmax = 0.2,
           ymin = 4,
           ymax = 18,
           fill = "green",
           alpha = 0.2) +
      annotate("text", 
               size = point_function_group_label_size,
               label = "Poisoned\narrowheads",
               hjust = 0,
           x = point_function_group_label_y,
           y = (18-4) /2 + 4) +
      annotate("rect", 
           xmin = 0.2,
           xmax = 0.3,
           ymin = 13,
           ymax = 53,
           fill = "blue",
           alpha = 0.2) +
      annotate("text", 
               size = point_function_group_label_size,
               label = "Arrowheads",
               hjust = 0,
           x = point_function_group_label_y,
           y = (53-13) /2 + 13) +
      annotate("rect", 
           xmin = 0.3,
           xmax = 0.4,
           ymin = 40,
           ymax = 76,
           fill = "orange",
           alpha = 0.2) +
      annotate("text", 
               size = point_function_group_label_size,
               label = "Dart tips",
               hjust = 0,
           x = point_function_group_label_y,
           y = (76-40) /2 + 40 ) +
      annotate("rect", 
           xmin = 0.4,
           xmax = 0.5,
           ymin = 44,
           ymax = 98,
           fill = "purple",
           alpha = 0.2) +
      annotate("text", 
               size = point_function_group_label_size,
               label = "Javelin",
               hjust = 0,
           x = point_function_group_label_y,
           y = (98-44) /2 + 44 ) +
     annotate("rect", 
           xmin = 0.5,
           xmax = 0.6,
           ymin = 88,
           ymax = 230,
           fill = "yellow",
           alpha = 0.2) +
      annotate("text", 
               label = "Thrusting\nspear",
               size = point_function_group_label_size,
               hjust = 0,
           x = point_function_group_label_y,
           y = (230-88) /2 + 88 ) +
  geom_boxplot(alpha = 0.1) +
  geom_quasirandom(alpha = 0.4,
                   size = 2.3) +
  coord_cartesian(xlim = c(-0.1,1)) +
  theme_bw(base_size = 6) +
  theme(axis.ticks.x = element_blank(),
        axis.text.x = element_blank(),
        axis.title.x = element_blank(),
        panel.grid.major = element_blank(), 
        panel.grid.minor = element_blank()
        ) +
  labs(y = "TCSA")
```

@@

### create column for "n = xx "
tcsa_raw <- tcsa %>% 
  group_by(raw_materials_top) %>% 
  add_tally() %>% 
  filter(n>1) %>% 
  mutate(label_raw = as.factor(paste0(raw_materials_top,' (n = ', n, ")"))) %>%   
  select(min_tcsa,
         raw_materials_top, 
       label_raw,
       n)   %>% 
  distinct_all()

>>>>

```{r}
library(readxl)
library(here)
library(tidyverse)
library(ggbeeswarm)
library(ggplot2)

@@

```{r, map, fig.cap="Korean Paleolithic sites mentioned in this study."}
# Facet by raw materials
korean_archaeological_site_locations <-
  read_excel(here::here("analysis/data/raw_data/TCSA_site_locations.xlsx"))

korean_archaeological_site_locations <-
  tibble::rowid_to_column(korean_archaeological_site_locations, "ID")

library(ggmap)
library(ggrepel)
library(legendMap)

map <-
  get_stamenmap(bbox = c(left = 124,
                         bottom = 33,
                         right = 	130,
                         top = 39),
                zoom = 10)

# map with site names next to the points
map_of_sites <-
  ggmap(map)  +
  geom_point(data = korean_archaeological_site_locations,
             aes(long_dd ,
                 lat_dd),
             colour = "red",
             size = 2) +
  # label points with site name
  geom_text_repel(data = korean_archaeological_site_locations,
                  aes(long_dd ,
                      lat_dd,
                      label = Site_name),
                  size = 2,
                  bg.color = "white",
                  bg.r = 0.15) +
  theme_minimal(base_size = 6) +
  labs(x = "Longitute",
       y = "Latitude") +
  legendMap::scale_bar(
    # edit these numbers to select a suitable location
    # for the scale bar where it does not cover
    # important details on the map
    lon = 124.5,
    lat = 33.5,
    legend_size = 2,
    # distance of one section of scale bar, in km
    distance_lon = 50,
    # height of the scale bar, in km
    distance_lat = 5,
    # distance between scale bar and units, in km
    distance_legend = 20,
    # units of scale bar
    dist_unit = "km",
    # add the north arrow
    orientation = TRUE,
    # length of N arrow, in km
    arrow_length = 60,
    # distance between scale bar & base of N arrow, in km
    arrow_distance = 50,
    # size of letter 'N' on N arrow, in km
    arrow_north_size = 10) +
  theme(axis.title.x = element_blank(),
        axis.title.y = element_blank())

# inset world map, from
# https://stackoverflow.com/a/62104396/1036500
library(maps)
library(magrittr)
library(maptools)
library(raster)
library(ggplot2)

#Defining a general CRS
mycrs <- "+proj=longlat +datum=WGS84 +no_defs"

#Using the original maps package, then converting map into SpatialPolygons object
world <- maps::map("world", fill=TRUE,  plot = FALSE) %$%
  maptools::map2SpatialPolygons(., IDs=names,proj4string=CRS(mycrs))

#The resulting map has self intersection problems so any further operation reports errors; using buffers of width 0 is a fast fix
while(rgeos::gIsValid(world)==FALSE){
  world <- rgeos::gBuffer(world, byid = TRUE, width = 0, quadsegs = 5, capStyle = "ROUND")
}

#Dissolving polygon's limits
world <- raster::aggregate(world)

worldplot <-
  ggplot() +
  geom_polygon(data = world,
               aes(x=long, y=lat,
                   group=group),
               fill='NA',
               color='black',
               size=0.1) +
  annotate("rect",
           xmin = 118,
           xmax = 137,
           ymin = 28,
           ymax = 47,
           fill = NA,
           colour = "red",
           size = 0.5
  ) +
  theme_void() +
  coord_fixed(1) +
  labs(x = "", y = "") +
  labs(x = NULL, y = NULL, title = NULL) +
  scale_x_continuous(expand = c(0, 0)) +
  scale_y_continuous(expand = c(0, 0)) +
  theme(panel.background = element_rect(fill = "white"),
        panel.border = element_blank(),
        axis.title.x=element_blank(),
        axis.text.x=element_blank(),
        axis.ticks.x=element_blank(),
        axis.title.y=element_blank(),
        axis.text.y=element_blank(),
        axis.ticks.y=element_blank())

# combine site map and inset map
library(cowplot)
ggdraw() +
  draw_plot(map_of_sites) +
  draw_plot(plot = worldplot,
            x = 0.6, # x location of inset placement
            y = -0.09, # y location of inset placement
            width = .4, # Inset width
            height = .35, # Inset height
            scale = 0.5 # Inset scale
  ) +
  theme(panel.background = element_rect(fill='white', colour="white"),
        plot.background = element_rect(fill='white', colour="white"))

@@

ggplot(tcsa,
        aes(0.3, 
            min_tcsa)) +
  # show regions for tools from Table 3 of Lomabrd 2021
  # https://www-sciencedirect-com.offcampus.lib.washington.edu/science/article/pii/S0277379121002286
    annotate("rect", 
           xmin = 0.1,
           xmax = 0.2,
           ymin = 4,
           ymax = 18,
           fill = "green",
           alpha = 0.2) +
      annotate("text", 
               size = point_function_group_label_size,
               label = "Poisoned\narrowheads",
               hjust = 0,
           x = point_function_group_label_y,
           y = (18-4) /2 + 4) +
      annotate("rect", 
           xmin = 0.2,
           xmax = 0.3,
           ymin = 13,
           ymax = 53,
           fill = "blue",
           alpha = 0.2) +
      annotate("text", 
               size = point_function_group_label_size,
               label = "Arrowheads",
               hjust = 0,
           x = point_function_group_label_y,
           y = (53-13) /2 + 13) +
      annotate("rect", 
           xmin = 0.3,
           xmax = 0.4,
           ymin = 40,
           ymax = 76,
           fill = "orange",
           alpha = 0.2) +
      annotate("text", 
               size = point_function_group_label_size,
               label = "Dart tips",
               hjust = 0,
           x = point_function_group_label_y,
           y = (76-40) /2 + 40 ) +
      annotate("rect", 
           xmin = 0.4,
           xmax = 0.5,
           ymin = 44,
           ymax = 98,
           fill = "purple",
           alpha = 0.2) +
      annotate("text", 
               size = point_function_group_label_size,
               label = "Javelin",
               hjust = 0,
           x = point_function_group_label_y,
           y = (98-44) /2 + 44 ) +
     annotate("rect", 
           xmin = 0.5,
           xmax = 0.6,
           ymin = 88,
           ymax = 230,
           fill = "yellow",
           alpha = 0.2) +
      annotate("text", 
               label = "Thrusting\nspear",
               size = point_function_group_label_size,
               hjust = 0,
           x = point_function_group_label_y,
           y = (230-88) /2 + 88 ) +
  geom_boxplot(alpha = 0.1) +
  geom_quasirandom(alpha = 0.4,
                   size = 2.3) +
  coord_cartesian(xlim = c(-0.1,1)) +
  theme_bw(base_size = 6) +
  theme(axis.ticks.x = element_blank(),
        axis.text.x = element_blank(),
        axis.title.x = element_blank(),
        panel.grid.major = element_blank(), 
        panel.grid.minor = element_blank()
        ) +
  labs(y = "TCSA")
```

@@

### create column for "n = xx "
tcsa_raw <- tcsa %>% 
  group_by(raw_materials_top) %>% 
  add_tally() %>% 
  filter(n>1) %>% 
  mutate(label_raw = as.factor(paste0(raw_materials_top,' (n = ', n, ")"))) %>%   
  dplyr::select(min_tcsa,
         raw_materials_top, 
       label_raw,
       n)   %>% 
  distinct_all()
